---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# Charting Test

Provides charting libraries for BrandsEye. 

# Installing

Installing the library mostly is about making sure that you have R (the tool that all this runs in) 
and RStudio (an interface for interacting with all of this) installed, and then installing the library.

1. Download and install first [R](https://cran.rstudio.com/) and then 
[RStudio](https://www.rstudio.com/products/rstudio/download/) .

2. You need to install the fonts that the library uses when plotting. These are [Open Sans](https://fonts.google.com/specimen/Open+Sans) 
and [Nunito Sans](https://fonts.google.com/specimen/Nunito+Sans) fonts, 
which if you don't have installed, you can get from Google Fonts.

3. You can install the this library using the `devtools` package. You should do this 
   from inside of RStudio, in the area called the Console. You can copy and paste
   the code below, and press enter to run it:
    ```{r eval=FALSE}
    # Install the devtools package
    install.packages("devtools")
    library(devtools)
    
    # Install the library
    install_github("brandseye/chartingtest")
    ```
4. The next step is to authenticate yourself. This lets the library know who
   you are and what accounts you have access to. You do that by supplying your
   API key, as in the code below. Your API key is like a password in to all of your
   accounts. Please do not share this with clients, since it would give them access to
   all of our accounts. You can find your API key by logging in to mash, and looking
   yourself up in the user list. Place your API key inbetween the quotes in the code below,
   and run it in the RStudio console.
    ```{r, eval = FALSE}
    # If you have never used brandseyer before, you probably need to authenticate
    # the first time you install this library. 
    brandseyer2::authenticate(key = "<my api key>", save = TRUE)
    ```

5. Finally, you can load the charting library by copying and pasting the line below. 

    ```{r, eval = FALSE}
    # Load the library
    library(chartingtest)
    ```

# Getting data

All data can be downloaded and saved as a CSV (or plotted) using a single line of R. For example,
here we get data for plotting volume against sentiment for the `QUIR01BA` account, using a particular
filter, and also asking to save the data. 

```{r, echo=FALSE}
library(chartingtest)
```

```{r eval=FALSE}
# Ask for data. Tell it that you want to save to file as well
volume_sentiment_metric("QUIR01BA", "published inthelast week and brand isorchildof 10006", save = TRUE)
```

And this is what the data would look like in R itself (there will be similar columns in the CSV).

```{r echo=FALSE}

library(chartingtest)
volume_sentiment_metric("QUIR01BA", "published inthelast week and brand isorchildof 10006")
```

# What data is available so far?

You can find a list of functions that can provide data for you online, [here](reference/index.html).

# The first time you use this

The first time that you use this library, you'll probably have to authenticate yourself
so that it knows who you are and what accounts you have access to. You can do that by getting
your API key from mash, and running

```{r, eval=FALSE}
brandseyer2::authenticate(key = "<my api key>", save = TRUE)
```

You only have to do this once. It will save your API key to reuse it again in the future.

# Adding fonts to R

If you're using the library for the first time, you'll need to add the required fonts. First download and install them on your machine:

- [Open Sans](https://fonts.google.com/specimen/Open+Sans) 
- [Nunito Sans](https://fonts.google.com/specimen/Nunito+Sans)

Then add them to R using the `extrafont` package:

```{r, eval=FALSE}
# Install the extrafont package
install.packages("extrafont")
library(extrafont)

# Import fonts into R
font_import(pattern="OpenSans")
font_import(pattern="NunitoSans")
```


# Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

## License

This is copyright BrandsEye, and licensed under the MIT license. See
the license files for details.
