---
title: "Example script"
author: "Lara Basson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example script}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here is an example script you can run to get a feel for how you might set up CSVs for a report.

## Set up your account code & filter

```{r}
# First you'll want to set an account code
code <- "QUIR01BA" 

# Then set a filter - remember to add a brand
filter <- "published inthelast week and relevancy is relevant and brand isorchildof 10006"
```

If you want to find brand IDs from an account, look at our article on finding [brands](brands.html) using R!

## Getting volume and sentiment breakdown (volume )

```{r}
library(chartingtest)

# Now you can get a breakdown of volume and sentiment (including net sentiment) by date
volume_sentiment_metric(code, filter)

# You can tell the function what to group by
volume_sentiment_metric(code, filter, group = "week")



```




## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
