---
title: "Setting up a script"
author: "Lara Basson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting up a script}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here is an example script you can run to get a feel for how you might set up CSVs for a report.

## Set up your account code & filter

Once you've set up an account code and filter, you can use this in your various metrics:

```{r }
# First you'll want to set an account code
code <- "QUIR01BA" 

# Then set a filter - remember to add a brand
filter <- "published inthelast week and relevancy is relevant and brand isorchildof 10006"
```

If you want to find brand IDs from an account, look at the article on finding [brands](brands.html) using R.


## Getting volume and sentiment

```{r, eval=FALSE}
# To use a function from chartingtest, you'll first need to load the library
library(chartingtest)

# Now you can get a breakdown of volume and sentiment (including net sentiment) by date
volume_sentiment_metric(code, filter)
```

```{r, echo=FALSE}
library(chartingtest)
knitr::kable(volume_sentiment_metric(code, filter) %>% dplyr::mutate(positivePercent=scales::percent(positivePercent), neutralPercent=scales::percent(neutralPercent), negativePercent=scales::percent(negativePercent)), digits=2, format = "html") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```


### Grouping by day, week or month

```{r, eval=FALSE}
# You can group by day, week or month
volume_sentiment_metric(code, filter, group = "week")
```

```{r, echo=FALSE}
knitr::kable(volume_sentiment_metric(code, filter) %>% dplyr::mutate(positivePercent=scales::percent(positivePercent), neutralPercent=scales::percent(neutralPercent), negativePercent=scales::percent(negativePercent)), digits=2) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```

## Saving to CSV
``` {r, eval=FALSE}
# To save to CSV, set save=TRUE - you'll be asked to enter a filename
volume_sentiment_metric(code, filter, group = "day", save=TRUE)

# If you want to run the code as part of a script, you can specify the file upfront and it will save automatically
volume_sentiment_metric(code, filter, group = "day", file="C:/Users/brandseye/Documents/volume_sentiment.csv")

```

## More examples

### Sentiment metric
```{r, eval=FALSE}
# Get data for the sentiment metric
sentiment_metric(code, filter)
```

``` {r, echo=FALSE}
knitr::kable(sentiment_metric(code, filter) %>% dplyr::mutate(Percentage=scales::percent(Percentage))) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```

### Stats metric
```{r, eval=FALSE}
# Get data for the stats metric
stats_metric(code, filter)
```

```{r, echo=FALSE}
knitr::kable(stats_metric(code, filter)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```

## Putting it all together

Here is an example of a script you might run to get all the CSVs for a particular report. In this example we will set the filter only once, but you could use multiple filters if you like, or add additional filtering to a particular metric.

*How to run the example:*

- Copy this code into a new file (File -> New File -> R Script) 
- Replace `PATH_TO_YOUR_FOLDER` with the folder where you'd like to save the CSVs, e.g. C:/Users/You/YourReport
- Give it a try by hitting _Run_

```{r, eval=FALSE}
library(chartingtest)

# Loading 'glue' so we can set the folder name once and then stick it together with the filename
library(glue)

# Set account code to use
code <- "QUIR01BA" 

# Set the filter to use
filter <- "published inthelast week and relevancy is relevant and brand isorchildof 10006"

folder <- "PATH_TO_YOUR_FOLDER"

# Get the volume breakdown
volume_sentiment_metric(code, 
                        filter, 
                        file = glue(folder, "/volume-metric.csv")) # join the folder name onto the file name

# Get the hourly breakdown
time_of_day_metric(code, 
                   filter, 
                   file = glue(folder, "/time-of-day.csv"))

# Top 10 authors
authors_metric(code, 
               filter, 
               truncateAt = 10, #Only give me the first 10 authors
               glue(folder, "/authors-metric.csv"))

# Top 10 sites
sites_metric(code, 
             filter, 
             truncateAt = 10, #Only give me the first 10 sites
             file = glue(folder, "/sites-metric.csv"))

# Sentiment breakdown
sentiment_metric(code, 
                 filter, 
                 file = glue(folder, "/sentiment-metric.csv"))

# Top 10 words
wordcloud_metric(code, 
                 filter, 
                 file = glue(folder, "/wordcloud-metric.csv"))
```



