---
title: "Setting up a script"
author: "Lara Basson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting up a script}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here is an example script you can run to get a feel for how you might set up CSVs for a report.

## Set up your account code & filter

Once you've set up an account code and filter, you can use this in your various metrics:

```{r }
# First you'll want to set an account code
code <- "QUIR01BA" 

# Then set a filter - remember to add a brand
filter <- "published inthelast week and relevancy is relevant and brand isorchildof 10006"
```

If you want to find brand IDs from an account, look at the article on finding [brands](brands.html) using R.


## Getting volume and sentiment

```{r, eval=FALSE}
# To use a function from chartingtest, you'll first need to load the library
library(chartingtest)

# Now you can get a breakdown of volume and sentiment (including net sentiment) by date
volume_sentiment_metric(code, filter)
```

```{r, echo=FALSE}
library(chartingtest)
knitr::kable(volume_sentiment_metric(code, filter), digits=2, format = "html") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```


### Grouping by day, week or month

```{r, eval=FALSE}
# You can group by day, week or month
volume_sentiment_metric(code, filter, group = "week")
```

```{r, echo=FALSE}
knitr::kable(volume_sentiment_metric(code, filter), digits=2) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```

## Saving to CSV
``` {r, eval=FALSE}
# To save to CSV, set save=TRUE - you'll be asked to enter a filename
volume_sentiment_metric(code, filter, group = "day", save=TRUE)

# If you want to run the code as part of a script, you can specify the file upfront and it will save automatically
volume_sentiment_metric(code, filter, group = "day", file="C:/Users/brandseye/Documents/volume_sentiment.csv")

```

## More examples

### Sentiment metric
```{r, eval=FALSE}
# Get data for the sentiment metric
sentiment_metric(code, filter)
```

``` {r, echo=FALSE}
knitr::kable(sentiment_metric(code, filter) %>% dplyr::mutate(Percentage=scales::percent(Percentage))) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```


### Stats metric
```{r, eval=FALSE}
# Get data for the stats metric
stats_metric(code, filter)
```

```{r, echo=FALSE}
knitr::kable(stats_metric(code, filter)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "responsive", "condensed"), full_width = F, font_size = 11)
```

For an 
